\section{Conclusions}
\label{chapter:conclusions}



Photo visualization is an eternal problem with lots of compromises. Big software companies sell the simple ways with big lists of photos, but many other ways have been explored for years, some more eccentric than others. Some more useful than others. We explored their good and bad points and selected the features we thought important. Made a user survey and fine tuned our vision and Eagle Eye was born.

Our work aimed at being useful to users who have a regular collection of photos on their computers and want a better way to view and learn more about them. We built a system that gives users a completely different view of their collection, by showing everything at the same time. While overwhelming at first, we have seen that users like it and, by already having knowledge about their own library, they can understand each group of photos, whether their photos were taken yesterday or ten years ago. From this, we allow users to change, reorder, filter, zoom and enjoy their pictures.

For this to be possible, we developed a system that extracts information from images and that can be expanded with more processes to obtain interesting and uncommonly seen information. This allows  users to observe their collection in a variety of ways, by selecting different information and filtering down to specific sets of images.


Although we didn't had time to implement many features we had in mind for an even better system, our user tests revealed that people liked the system, giving it a moderately good rating of 75 in a scale of 0 to 100. 

We think we have a solid concept that, with some more development, could be made as an application that could actually be released to the public.


% section concluding (end)




\subsection{Future Work} % (fold)
\label{future_work}

During the realization of this work, many ideas popped in our minds but we didn't had the time to work on them. The system needs some consolidation, specially on the backend. The feature extraction plugins should also be improved, like the color extraction, and a few could be added. The visualization should be improved, by providing more help to users, by increasing the features and by fixing the bugs. It would also be interesting if we could connect Eagle Eye to calendaring and location-based services to obtain more event and location data for photos.